Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-29 Paper/MSRChallenge2017.tex
changed the not shown and added citations to introduction

This previous work has focused on the predicted acceptance of open source \emph{pull
requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
in a single project. %TODO: should there be a ref here?
By contrast,  we are interested in analyzing contribution quality 
in \emph{continuous integration} across multiple open source projects.  While 
pull request
quality is ultimately determined through manual inspection, continuous
integration uses test cases to automatically assess commit quality,
and thus may provide different quality predictors. 
We investigate the factors related to continuous integration build success
across open source projects.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

The decision tree results suggested that core team membership is
important to classifying build success (results not shown), and thus we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set; 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set,
and 64.70\% (25479/39381) of the builds passed.  The difference in success rate
is statistically significant (the p-value from a Fisher exact
test is 0.0000), suggesting that it is extremely unlikely to have occurred by
chance. Thus, in our dataset, core team 
members are more
likely to have a successful build integration than non-core team developers, likely
because core team members are naturally more familiar with the 
codebase.

>>>>

This previous work has focused on the predicted acceptance of open source \emph{pull
requests}~\cite{tsay14icse, tsay14fse} and \emph{continuous integration} builds
in a single project~\cite{Hassan06,Kwan11,Wolf09}. 
By contrast,  we are interested in analyzing contribution quality 
in \emph{continuous integration} across multiple open source projects.  While 
pull request
quality is ultimately determined through manual inspection, continuous
integration uses test cases to automatically assess commit quality,
and thus may provide different quality predictors. 
We investigate the factors related to continuous integration build success
across open source projects.
In this study, we analyze a large set of technical and social attributes 
and how these can be used to predict a contribution's quality, measured by the
success of build integration jobs.
We performed this analysis on a large corpus of open source projects
which incorporated continuous integration in their development practice. 
When a contribution to these projects passes integration tests, 
it suggests that the project developers
might have confidence in the changes. 
Thus, we use the commit's build integration status as a proxy for its quality.

@@

The decision tree results suggested that core team membership is
important to classifying build success (in supplemental material), and thus 
we investigated the question
directly. 
We classified the build success rate for
core team members and non-core team members using the data set without 
downsampling.  We found that core team members
triggered 89.39\% (331827/371208) of the builds in the data set; 75.58\%
(250808/331827) of those builds
passed.  Non-core team members triggered 10.61\% (39381/371208) of the builds 
in the data set,
and 64.70\% (25479/39381) of the builds passed.  The difference in success rate
is statistically significant (the p-value from a Fisher exact
test is 0.0000), suggesting that it is extremely unlikely to have occurred by
chance. Thus, in our dataset, core team 
members are more
likely to have a successful build integration than non-core team developers, likely
because core team members are naturally more familiar with the 
codebase.
